\sysfull

### 2018-04-14 paper/newCoalescing.tex
added placeholder for partial commit
remove the history our algo and its fig

@@

\subsection{SC: Slow Coalescing}
\label{subsec:slowCoalescing}

@@

\subsection{HC: History-aware Coalescing}
\label{subsec:hCCoalescing}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/HCCoal}%coalescing_timeline
	\caption{The History-aware coalescing algorithm  updates its coalescing target}
	\label{fig:HCCoal}
\end{figure}

The History-aware algorithm uses its recent execution history as metric to estimate the optimal coalesce task size. Relying on the history of execution enables this algorithm to react very quickly to discharge rates variation.

>>>>

\subsection{Task Coalescing}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coal_Intro_Figure.pdf}%coalescing_timeline
	\caption{ When $N$ tasks coalesced $N-1$ commit operations is skipped.}
	\label{fig:coalIntro}
\end{figure}

When incoming energy is sufficient to run multiple consecutive tasks,
committing state after each task is wasteful. \sys mitigates this
waste by deferring the expensive commits and performing them in a
batch. In the resulting execution, several tasks are \emph{merged} into a
single virtual task---a process we call \emph{coalescing}. 
%
When $N$ tasks are coalesced, $N-1$ boundaries are crossed and some number of
pages are dirtied. The first $N-2$ executions of \transition statement skip
committing dirty pages to non-volatile memory, leaving the work of committing
pages modified by any of the $N$ tasks to the statement $N-1$.
Coalescing is likely to reduce the total number of non-volatile memory
accesses, because when coalesced tasks access the same pages of data, only the
last version of the page needs to be committed.  \textcolor{red}{maybe is possible to demonstrate with data? count number of executed non-volatile vs volatile accesses}

@@

\subsubsection{SC: Slow Coalescing}
\label{subsec:slowCoalescing}

@@

% \subsubsection{HC: History-aware Coalescing}
% \label{subsec:hCCoalescing}

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\columnwidth]{figures/HCCoal}%coalescing_timeline
% 	\caption{The History-aware coalescing algorithm  updates its coalescing target}
% 	\label{fig:HCCoal}
% \end{figure}

% The History-aware algorithm uses its recent execution history as metric to estimate the optimal coalesce task size. Relying on the history of execution enables this algorithm to react very quickly to discharge rates variation.
